Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2014-10-05 unstructured.tex
2014.10.05 (Vassilis) Clean-up, rewording and reviewing the unstructured section. Efficiency, overhead and scalability definitions reworked in background section.

In this section, we present algorithms that tackle the topology mismatch
problem in unstructured \p\ networks. We classify them based on their
use of the overlay structure, their message forwarding scheme 
for peer communication and the techniques they use for detecting
proximity, to be used to optimize their overlay topology.

@@

To improve over {\sl Gnutella}'s ``blind flooding'' approach,
\cite{YG-M2002} proposed a practical and easy to implement solution 
weaved around three different message forwarding methods:
\emph{iterative deepening},
\emph{directed BFS}, and \emph{local indices}.

In \emph{iterative deepening}, 
%(see Figure~\ref{figure:dbfs:iterdeep})
the search is
performed on a BFS tree with multiple preset depths. 
The depth limit is iteratively increased by the source node for each query, 
based on the quality of the results. 
The source node may issue a new request with increased depth limit
that will trigger the nodes at the last depth level to resume the search. 
The iterative approach avoids restarting the entire search process 
from scratch at each iteration and reduces the load on the nodes of 
the upper levels of the tree. 
Its major drawback is the delay between successive iterations, as the
source-node has to examine the results at each attempt before deciding to
either quit or ``unfreeze'' the query.

The \emph{directed BFS}
tries to avoid the aforementioned delay by forwarding 
query messages only to a selected subset of available neighbors. The selection
criteria varies, from the number of results received previously or the distance
in terms of hops traveled to locate these results, to the bandwidth, or the
query load of the neighbor. That way, fewer nodes are visited but quality of
query responses is maintained, to a large degree, on the premise that the
selected heuristics can direct the search to the right path.
%
In \emph{local indices},
each node indexes data within a radius of $r$ hops and uses 
this local index to answer queries % on behalf of them 
without generating additional traffic. Local indices
greatly reduce the aggregate bandwidth usage of the network and 
improve query efficiency. However, updating such indices in 
the presence of frequent node joins/departures 
may introduce significant overhead should the radius is kept broad.
%%
Below, we outline how the techniques in~\cite{YG-M2002}
fare against the $3$ major performance criteria 
of Section~\ref{section:background}.
% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process.
low &
% the process in not started from the beginning at each iteration step. For
% popular files this can substantially reduce overhead but for less popular
% ones, its performance might be uncertain due to the repeated restart of
% flooding
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spiral).
medium &
% BFS is Gnutella's non efficient communication method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated across the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Gia}

The key objective of the {\sl Gia} system~\cite{CRBLS2003} is 
to help alleviate the scalability omnipresent
in unstructured \p\ file-sharing systems.
At first, {\sl Gia} replaced {\sl Gnutella}'s blind flooding 
with random walks.
Although this adoption was 
a step in the right direction \cite{LCCLS2002},
issuing a single copy of the query within the network
effectively reduces the search scope and may negatively affect 
the success rate of the query in question.
To overcome this limitation, {\sl Gia} introduces
a token-based flow control mechanism 
that gradually redirects queries to nodes which are more
likely to answer. This flow control mechanism also helps prevent node
overloading as each peer ``announces'' the number of query requests it 
can handle, in terms of tokens, to its neighbors; to this end, 
peers only forward query requests to nodes that they previously
received tokens from. Further refinement to the search mechanism is the
support for \emph{one--hop replication} of pointers to content.
{\sl Gia} also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc., of \p\ nodes and uses this
information when connecting nodes to each other.
By using a topology adaptation algorithm, 
{\sl Gia} places low capacity nodes within 
short proximity to peers with high performance features.
This topology adaptation algorithm is based on the metric 
each node maintains about its satisfaction --ranging between $0$ and $1$--
for the neighbors it finds itself associated with. 
Through message exchange, a peer can establish new connections 
or drop superseded ones in order to improve its satisfaction.
Despite the fact that {\sl Gia}'s topology adaptation algorithm 
that primarily focuses on the satisfaction of peers improves the network's 
scalability it falls short in addressing the mismatch problem
as considerations for the underlying network are not handled in explicit
terms \cite{LXLNZ2005}. Moreover it reduces the search scope, exhibits poor
performance in the worst case when matching data is not found quickly
\cite{PR2004,HJ2004} and can potentially build  disconnected topologies
\cite{MBL2006}.
%
In terms of the $3$ stated criteria, {\sl Gia}'s approach is as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Reduces the search scope.
medium &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
}
\end{center}

@@

The \emph{neighbor comparison and selection} component defines that a peer $S$
probe all his $2$-hops away neighbors (a set denoted as $ N^2(S)$) not probed
thus far. Let $P$ be a $1$-hop distance neighbor of $S$, and $Q$ be a probed
peer by $S$. When $S$ receives a message piggybacked with message $PM_{PQ}$, 
% we identify the following cases.  %%AD put it passive as below.. 
the following $2$ cases are identified:

@@

As discussed above, \emph{THANCS} is fully distributed and needs only minimum knowledge
of, at most, a $2$-hop distant peers. This features renders 
the method a good candidate for large overlay networks. 
Also its topology adaptation helps construct a well fit overlay
with respect to the underlying network--at least with respect to network
distances. In addition, will-cut list and distance caches (which store already
probed peers) minimize the unnecessary messages for the network maintenance.
%%
In \cite{HLY2010}, the simulation-derived results of \emph{THANCS} as far
average broadcast delay and overlay improvement guarantees are discussed;
overall, \emph{THANCS} fares as follows regarding the $3$ stated criteria:
%%AD rephrased more diplomatically the following as above.. 
% There are works in the literature though that criticize, through simulation
% results, the algorithm's average broadcast delay and overlay improvement
% guarantee \cite{HLY2010}.
% These characteristics are depicted to the $3$ evaluation criteria we use in this
% survey as follows:
%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% 
medium &
% trivial overhead compared to the query cost savings and its convergent speed
% is faster than minimum spanning tree approaches so less overall overhead cost.
low &
% completely distributed and needs no global knowledge,
high
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \emph{Hops Adaptive Neighbor Discovery (HAND)} algorithm~\cite{CLZHC2006}
uses a fully-distributed triple--hop adjustment strategy, applied to a network
graph $G$ in order to create an optimal graph $G^{*}$, free of the implications
of topology mismatch. This optimality is attained if all peer hop 
sequences $(v_1, v_2, \ldots, v_k)$ of $G$ exist in $G^{*}$ and are in the same
order. The latter indicates that in practice triple sequences $(v_1, v_2, v_3)$
are used. A mismatch is detected as follows: should we want to verify
a sequence, say $v_2-v_1-v_3$, two probing messages are dispatched from $v_1$ to
$v_2$ and $v_3$ and yield delays of $x$ and $z$ respectively.
%
When the probing message arrives at $v_2$, it gets forwarded
directly to $v_3$. 
Similarly, the message reaching $v_3$ is directly forwarded to $v_2$.
The above two forwarding actions seek to quantify 
the corresponding delays of $(v_2,v_3)$ and $(v_3,v_2)$ 
% physical paths denoted by $y$. 
for the physical path $y$.
%%AD check above... it is one path (not paths right?)
%%
If $y=z-x\pm\varepsilon$, the sequence $v_2-v_1-v_3$ is mismatched and should
be adjusted to $v_1-v_2-v_3$ by deleting edge $(v_1,v_3)$ and 
then adding a new $(v_2,v_3)$. 
If $y=x-z\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and
should be adjusted to $v_1-v_3-v_2$ by deleting edge $(v_1,v_2)$ and adding a
new $(v_3,v_2)$. 
The  $\varepsilon$ is a small positive real number denoting
additional delays caused by possible forwarding and jitter delays. 
%%
The advantages of \emph{HAND} are that it
\begin{inparaenum}[\itshape i\upshape)]
  \item does not need any clock synchronization,
  \item is a fully distributed algorithm.
  \item involves low traffic overhead,
  \item can be used in dynamic \p\ environments, and 
  \item furnishes low query response times.
\end{inparaenum}
%
% TODO: SOME DISCUSSION
%
%Measurements conducted for evaluation purposes showed that in a static
% environment the algorithm can effectively decrease traffic cost by about 77
%percent and shorten the query response time by about 49 percent in less than
%two minutes. In a dynamic environment it shows similar behavior and with the
%size of the overlay network having little impact on the effectiveness of the
%algorithm. Compared to LTM both algorithms have almost the same traffic
%reduction rate, however on the response time reduction rate HAND has a higher
%one by about 4 percent. The traffic overhead of HAND is much less than that of
%LTM by an average of 55 percent.
In terms of the $3$ stated criteria, \emph{HAND} fares as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% similar traffic reduction rate savings to LTM
medium &
% The traffic overhead of HAND is much less than that of LTM by an average of
% 55 percent.
low &
% no clock syncing needed, fully distributed and with low control overhead the
% algorithm can be considered scalable.
high
\end{tabular}
}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The main objective of the \emph{Biased Neighbor Selection (BNS)} 
approach~\cite{BCCMSBZ2006} is to 
strengthen {\sl BitTorrent}'s~\cite{c_bittorrent_2003} locality 
by carefully choosing most of the neighbors of a peer to come from 
the same \emph{ISP}, while simultaneously adhering to the near-optimal
download performance of the protocol.
%%
By and large, {\sl BitTorrent} deploys mechanisms that have proved
aggressive to \emph{ISP} networking and accounting as they function 
in a ``without-borders'' approach. 
The default {\sl BitTorrent} specification
designates $35$ connections for each peer regardless if such connections are
placed within or outside the borders of the \emph{ISP} that hosts the node.
%%
\emph{BNS} proposes that only $k$ out of these $35$ connections be
established with nodes beyond the {\it ISP}-borders;
the $k$ connections offer an extended and ``global'' view of 
the network at large and seek to strike a balance between 
the load imposed inside and outside the \emph{ISP}.
The latter refrains peers from exchanging traffic through
expensive network links should there exist alternative local connections
offering the required services. 
%%
\emph{BNS} is realized through 
\begin{inparaenum}[1)]
\item
the modification of the tracker so that 
\emph{ISP}-local resources are rapidly identified
\item
the use of \p--traffic--shaping devices on \emph{ISP} edge--routers. 
\end{inparaenum}
%%
In~\cite{BCCMSBZ2006}, a combination of 
biased neighbor selection along with bandwidth throttling
and caching techniques for near-optimal lookup results is proposed. 
The effectiveness of \emph{BNS} is debated 
in~\cite{RTLCGZ2010} where experimental results suggest that 
most peers in a swarm reside in different authonomous systems (\emph{AS}s).
%%AD AS = autonomous systems??? - put it so. First time discussed!
Consequently, clients frequently do not have enough peers to leverage
intra-\emph{AS} connections \cite{RTLCGZ2010}.
%%AD rephrased as above - what is AS??? Acronym... 
% On the other hand, the effectiveness of \emph{BNS}
% is arguable by other studies, whose
% experimental results suggest that most peers in a swarm reside in different ASs,
% thus a client in most of the cases does not have enough peers to leverage
% intra-AS connections \cite{RTLCGZ2010}. 
Moreover, \emph{BNS} deployment
requires knowledge of \emph{ISP} network mappings and awareness of possible
changes that occur in the infrastructure limiting its widespread adoption; the
following table qualitatively depicts the expected behavior of \emph{BNS}:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% inter-ISP cost minimized while retaining the near optimal performance of
% BitTorrent download.
high &
% this info is taken at swarm join
low &
% trackers should maintain and update proximity info/proximity info is
% retrieved from special hardware.
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{Ono}~\cite{CB2008} is a protocol that helps contain
{\sl BitTorrent} traffic within individual \emph{ISP}s
and enhances the downloading rates by favoring connections
within the borders of a single autonomous system. Contrary to
\emph{BNS}~\cite{BCCMSBZ2006},
\emph{Oro} leads to improved performance 
without requiring any explicit cooperation between 
\emph{ISP} subscribers or any additional
infrastructure and network topology information.
\emph{Oro}'s selection approach is 
landmark-based and leverages existing {\sl CDN}-infrastructure 
for peer distance estimation. {\sl CDN}s already use both static (i.e.,
geographical, \emph{IP}-clustering) and dynamic (i.e., network delay measurement)
information for their replica selection. Thus, the algorithm leverages the
observation that peers that are redirected to a specific {\sl CDN} replica does not
only mean that these are close by this replica but to each other as well.
%%
The redirection behavior is modeled in terms of \emph{ratio map}, 
a vector of \emph{$<$replica-server,ratio$>$} tuples, where \emph{ratio} is
the percentage of times the {\sl CDN} redirects the peer 
to the specific \emph{replica-server}.
%%
The protocol's bootstrapping phase consists of the incoming peer performing
{\sl DNS} lookups to {\sl CDN}-names to build its redirection information.
%%
Initially, the {\sl DNS} polling interval is set to $30$ seconds 
and increases by $1$ minute every time redirection information 
to the {\sl CDN} remains unchanged after the lookup.
The {\sl DNS} polling interval is halved if pertinent 
redirection information has changed.
To avoid the bootstrapping phase when the \emph{ratio map} 
is sufficiently fresh, 
\emph{Oro} persists the map after the end of a {\sl BitTorrent} session.
%%
Experimentation with \emph{Oro} yields minimization of
inter-\emph{ISP} traffic costs and achieves near optimal performance 
of {\sl BitTorrent} download~\cite{BCCMSBZ2006}.
The \emph{ISP}-friendly design of \emph{Ono} however has been questioned when 
it comes to Internet-scale~\cite{PMJKA2009,LCLX2009,CLYSR2011};
its qualitative rating stands as follows:
%%AD rephrased as above...
% Even though the results in the paper claim minimization of inter-ISP traffic
% cost while enhancing the, already, near optimal performance of BitTorrent
% download, similar to \cite{BCCMSBZ2006}, this ISP-friendly design of \emph{Ono}
% is questioned, especially on a Internet-scale-basis \cite{PMJKA2009,LCLX2009,CLYSR2011}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Authors claim minimization of inter-ISP traffic cost while enhancing the,
% already, near optimal performance of BitTorrent download.
medium &
% periodic DNS lookups and CDN redirection imposes medium control overhead to
% the method.
medium &
% the use of CDNs make the approach not fully distributed thus less scalable
low
\end{tabular}
}
\end{center}

>>>>

In this section, we present algorithms that tackle the topology mismatch
problem in unstructured \p\ networks. We classify them based on their
use of the overlay structure, their message forwarding scheme 
for peer communication and the techniques they use for detecting
proximity.

@@

To improve over {\sl Gnutella}'s ``blind flooding'' approach,
\cite{YG-M2002} proposed a practical and easy to implement solution 
weaved around three different message forwarding methods, namely
\emph{iterative deepening}, \emph{directed BFS} and \emph{local indices}.

In \emph{iterative deepening}, 
%(see Figure~\ref{figure:dbfs:iterdeep})
the search is
performed on a BFS tree with multiple preset depths. 
The depth limit is iteratively increased by the source node for each query, 
based on the quality of the results. 
The source node may issue a new request with increased depth limit
that will trigger the nodes at the last visited depth level to resume the
search thus avoiding restart of the entire search process and consequently 
reducing the load on the nodes of the upper levels of the tree. 
Its major drawback is the delay between successive iterations, as the
source-node has to examine the results at each attempt before deciding to
either quit or ``unfreeze'' the query.

The \emph{directed BFS}
tries to avoid the aforementioned delay by forwarding 
query messages only to a selected subset of available neighbors. The selection
criteria varies, from the number of results received or the distance (hops)
traveled to locate these results, to the bandwidth, or the
query load of the neighbor. That way, fewer nodes are visited but quality of
query responses is maintained, to a large degree, on the premise that the
selected heuristics can direct the search to the right path.
%
In \emph{local indices},
each node indexes data hosted by neighboring nodes within a radius of $r$ hops
and uses this local index to answer queries on behalf of other nodes.
That way, local indices,
greatly reduce the aggregate bandwidth usage of the network and 
improve query efficiency. However, updating such indices in 
the presence of frequent node joins/departures 
may introduce significant overhead should the radius is kept broad.
%%
Below, we outline how the techniques in~\cite{YG-M2002}
fare against the $3$ major performance criteria 
of Section~\ref{section:background}.

\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process.
low &
% the process in not started from the beginning at each iteration step. For
% popular files this can substantially reduce overhead but for less popular
% ones, its performance might be uncertain due to the repeated restart of
% flooding
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spiral).
medium &
% BFS is Gnutella's non efficient communication method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated across the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Gia}
The key objective of the {\sl Gia} system~\cite{CRBLS2003} is 
to help alleviate the scalability omnipresent
in unstructured \p\ file-sharing systems.
At first, {\sl Gia} replaced {\sl Gnutella}'s blind flooding 
with random walks.
Although this adoption was 
a step in the right direction \cite{LCCLS2002},
issuing a single copy of the query within the network
effectively reduces the search scope and may negatively affect 
the success rate of the query in question.
To overcome this limitation, {\sl Gia} introduces
a token-based flow control mechanism 
that gradually redirects queries to nodes which are more
likely to answer. This flow control mechanism also helps prevent node
overloading as each peer ``announces'' the number of query requests it 
can handle, in terms of tokens, to its neighbors; to this end, 
peers only forward query requests to nodes that they previously
received tokens from. Further refinement to the search mechanism is the
support for \emph{one--hop replication} of pointers to content.
{\sl Gia} also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc., of \p\ nodes and uses this
information when connecting nodes to each other.
By using a topology adaptation algorithm, 
{\sl Gia} places low capacity nodes within 
short proximity to peers with high performance features.
This topology adaptation algorithm is based on the metric 
each node maintains about its satisfaction --ranging between $0$ and $1$--
for the neighbors it finds itself associated with. 
Through message exchange, a peer can establish new connections 
or drop superseded ones in order to improve its satisfaction.
Despite the fact that {\sl Gia}'s topology adaptation algorithm 
that primarily focuses on the satisfaction of peers improves the network's 
scalability it falls short in addressing the mismatch problem
as considerations for the underlying network are not handled in explicit
terms \cite{LXLNZ2005}. Moreover it reduces the search scope, exhibits poor
performance in the worst case when matching data is not found quickly
\cite{PR2004,HJ2004} and can potentially build  disconnected topologies
\cite{MBL2006}.
%
In terms of the $3$ stated criteria, {\sl Gia}'s approach is as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Reduces the search scope.
medium &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
}
\end{center}

@@

The \emph{neighbor comparison and selection} component defines that a peer $S$
probes all his $2$-hops away neighbors (a set denoted as $ N^2(S)$) not probed
thus far. Let $P$ be a $1$-hop distance neighbor of $S$, and $Q$ be a probed
peer by $S$. When $S$ receives a message piggybacked with message $PM_{PQ}$, 
the following $2$ cases are identified:

@@

As discussed above, \emph{THANCS} is fully distributed and needs only minimum knowledge
of, at most, a $2$-hop distant peers. This features renders 
the method a good candidate for large overlay networks. 
Also its topology adaptation helps construct a well fit overlay
with respect to the underlying network--at least with respect to network
distances. In addition, will-cut list and distance caches (which store already
probed peers) minimize the unnecessary messages for the network maintenance.
%%
In \cite{HLY2010}, the simulation-derived results of \emph{THANCS} as far
average broadcast delay and overlay improvement guarantees are discussed;
overall, \emph{THANCS} fares as follows regarding the $3$ stated criteria:

%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% 
medium &
% trivial overhead compared to the query cost savings and its convergent speed
% is faster than minimum spanning tree approaches so less overall overhead cost.
low &
% completely distributed and needs no global knowledge,
high
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \emph{Hops Adaptive Neighbor Discovery (HAND)} algorithm~\cite{CLZHC2006}
uses a fully-distributed triple--hop adjustment strategy, applied to a network
graph $G$ in order to create an optimal graph $G^{*}$, free of the implications
of topology mismatch. This optimality is attained if all peer hop 
sequences $(v_1, v_2, \ldots, v_k)$ of $G$ exist in $G^{*}$ and are in the same
order. The latter indicates that in practice triple sequences $(v_1, v_2, v_3)$
are used. A mismatch is detected as follows: should we want to verify
a sequence, say $v_2-v_1-v_3$, two probing messages are dispatched from $v_1$ to
$v_2$ and $v_3$ and yield delays of $x$ and $z$ respectively.
%
When the probing message arrives at $v_2$, it gets forwarded
directly to $v_3$. 
Similarly, the message reaching $v_3$ is directly forwarded to $v_2$.
The above two forwarding actions seek to quantify 
the corresponding delays of $(v_2,v_3)$ and $(v_3,v_2)$
for the physical path $y$.
%%
If $y=z-x\pm\varepsilon$, the sequence $v_2-v_1-v_3$ is mismatched and should
be adjusted to $v_1-v_2-v_3$ by deleting edge $(v_1,v_3)$ and 
then adding a new $(v_2,v_3)$. 
If $y=x-z\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and
should be adjusted to $v_1-v_3-v_2$ by deleting edge $(v_1,v_2)$ and adding a
new $(v_3,v_2)$. 
The  $\varepsilon$ is a small positive real number denoting
additional delays caused by possible forwarding and jitter delays. 
%%
The advantages of \emph{HAND} are that it
\begin{inparaenum}[\itshape i\upshape)]
  \item does not need any clock synchronization,
  \item is a fully distributed algorithm.
  \item involves low traffic overhead,
  \item can be used in dynamic \p\ environments, and 
  \item furnishes low query response times.
\end{inparaenum}
%
% TODO: SOME DISCUSSION
%
%Measurements conducted for evaluation purposes showed that in a static
% environment the algorithm can effectively decrease traffic cost by about 77
%percent and shorten the query response time by about 49 percent in less than
%two minutes. In a dynamic environment it shows similar behavior and with the
%size of the overlay network having little impact on the effectiveness of the
%algorithm. Compared to LTM both algorithms have almost the same traffic
%reduction rate, however on the response time reduction rate HAND has a higher
%one by about 4 percent. The traffic overhead of HAND is much less than that of
%LTM by an average of 55 percent.
In terms of the $3$ stated criteria, \emph{HAND} fares as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% similar traffic reduction rate savings to LTM
medium &
% The traffic overhead of HAND is much less than that of LTM by an average of
% 55 percent.
low &
% no clock syncing needed, fully distributed and with low control overhead the
% algorithm can be considered scalable.
high
\end{tabular}
}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The main objective of the \emph{Biased Neighbor Selection (BNS)} 
approach~\cite{BCCMSBZ2006} is to 
strengthen {\sl BitTorrent}'s~\cite{c_bittorrent_2003} locality 
by carefully choosing most of the neighbors of a peer to come from 
the same \emph{ISP}, while simultaneously adhering to the near-optimal
download performance of the protocol.
%%
By and large, {\sl BitTorrent} deploys mechanisms that have proved
aggressive to \emph{ISP} networking and accounting as they function 
in a ``without-borders'' approach. 
The default {\sl BitTorrent} specification
designates $35$ connections for each peer regardless if such connections are
placed within or outside the borders of the \emph{ISP} that hosts the node.
%%
\emph{BNS} proposes that only $k$ out of these $35$ connections be
established with nodes beyond the {\it ISP}-borders;
the $k$ connections offer an extended and ``global'' view of 
the network at large and seek to strike a balance between 
the load imposed inside and outside the \emph{ISP}.
The latter refrains peers from exchanging traffic through
expensive network links should there exist alternative local connections
offering the required services. 
%%
\emph{BNS} is realized through 
\begin{inparaenum}[1)]
\item
the modification of the tracker so that 
\emph{ISP}-local resources are rapidly identified
\item
the use of \p--traffic--shaping devices on \emph{ISP} edge--routers. 
\end{inparaenum}
%%
In~\cite{BCCMSBZ2006}, a combination of 
biased neighbor selection along with bandwidth throttling
and caching techniques for near-optimal lookup results is proposed. 
The effectiveness of \emph{BNS} is debated 
in~\cite{RTLCGZ2010} where experimental results suggest that 
most peers in a swarm reside in different authonomous systems (\emph{AS}s).
Consequently, clients frequently do not have enough peers to leverage
intra-\emph{AS} connections \cite{RTLCGZ2010}.
Moreover, \emph{BNS} deployment
requires knowledge of \emph{ISP} network mappings and awareness of possible
changes that occur in the infrastructure limiting its widespread adoption; the
following table qualitatively depicts the expected behavior of \emph{BNS}:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% inter-ISP cost minimized while retaining the near optimal performance of
% BitTorrent download.
high &
% this info is taken at swarm join
low &
% trackers should maintain and update proximity info/proximity info is
% retrieved from special hardware.
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{Ono}~\cite{CB2008} is a protocol that helps contain
{\sl BitTorrent} traffic within individual \emph{ISP}s
and enhances the downloading rates by favoring connections
within the borders of a single autonomous system. Contrary to
\emph{BNS}~\cite{BCCMSBZ2006},
\emph{Oro} leads to improved performance 
without requiring any explicit cooperation between 
\emph{ISP} subscribers or any additional
infrastructure and network topology information.
\emph{Oro}'s selection approach is 
landmark-based and leverages existing {\sl CDN}-infrastructure 
for peer distance estimation. {\sl CDN}s already use both static (i.e.,
geographical, \emph{IP}-clustering) and dynamic (i.e., network delay measurement)
information for their replica selection. Thus, the algorithm leverages the
observation that peers that are redirected to a specific {\sl CDN} replica does not
only mean that these are close by this replica but to each other as well.
%%
The redirection behavior is modeled in terms of \emph{ratio map}, 
a vector of \emph{$<$replica-server,ratio$>$} tuples, where \emph{ratio} is
the percentage of times the {\sl CDN} redirects the peer 
to the specific \emph{replica-server}.
%%
The protocol's bootstrapping phase consists of the incoming peer performing
{\sl DNS} lookups to {\sl CDN}-names to build its redirection information.
%%
Initially, the {\sl DNS} polling interval is set to $30$ seconds 
and increases by $1$ minute every time redirection information 
to the {\sl CDN} remains unchanged after the lookup.
The {\sl DNS} polling interval is halved if pertinent 
redirection information has changed.
To avoid the bootstrapping phase when the \emph{ratio map} 
is sufficiently fresh, 
\emph{Oro} persists the map after the end of a {\sl BitTorrent} session.
%%
Experimentation with \emph{Ono} yields minimization of
inter-\emph{ISP} traffic costs and achieves near optimal performance 
of {\sl BitTorrent} download~\cite{BCCMSBZ2006}.
The \emph{ISP}-friendly design of \emph{Ono} however has been questioned when 
it comes to Internet-scale~\cite{PMJKA2009,LCLX2009,CLYSR2011};
its qualitative rating stands as follows:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Authors claim minimization of inter-ISP traffic cost while enhancing the,
% already, near optimal performance of BitTorrent download.
medium &
% periodic DNS lookups and CDN redirection imposes medium control overhead to
% the method.
medium &
% the use of CDNs make the approach not fully distributed thus less scalable
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Locality-Awareness in BitTorrent-like P2P Applications}
In~\cite{LCLX2009}, three techniques that 
``inject'' locality awareness in {\sl BitTorrent}-like applications are discussed.
The first \emph{macroscopic-level} technique
focuses on improving the neighbor selection process. 
When a peer asks a tracker to join, 
the later sorts its swarm peers according to
their hop-count distance from the requesting peer 
send out the top-$k$ list of nodes (e.g., $k$=$50$).
%%
The second technique, applied in an \emph{intermediate-level}, manipulates
{\sl BitTorrent}'s chocking/unchocking mechanism. A peer unchockes its $4$
closest, in terms of 
autonomous system hop-count, interested neighbors. 
The same applies also when the peer turns to 
the seeding state;  this  \emph{intermediate-level} approach favors
least distance and is in contrast to the original {\sl BitTorrent} 
implementation which favors uploading speed.
%%
The last technique operates at a \emph{microscopic-level} by chosing to pick
the next chunk to download based on a locality-first policy; this picks first
the chunk that is closer, as opposed to {\sl BitTorrent}'s rare-first chunk
picking policy.
%%VM I once more reworded the above, seemed to complex to me
The distance value of a chunk is computed as the mean
value of the distances of the peers that posses it.
Through experimentation on a real-world Internet topology simulated in
{\sf PlanetLab}, the locality-based approach achieves traffic optimization.
Nevertheless, it does not do that well when compared with the
random approach of the standard {\sl BitTorrent} protocol.

All $3$ techniques in~\cite{LCLX2009} seek to harness 
the locality of the basic functions of the
{\sl BitTorrent} protocol. 
Even though they do not restructure the network to map
better to the underlying infrastructure, they favor the intra-\emph{AS} 
over inter-\emph{AS} communications thus, reducing the overall communication cost.
Again, there is a trade-off between reducing inter-domain
traffic and fairness among peers in terms of the data the peers upload~\cite{LCLX2009};
as far as the $3$ criteria, the overall approach fares as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% minimization of inter-AS traffic but unfair among peers.
medium &
% info (AS hop distances) acquired at swarm join
low &
% does not result in a better map to the underlying topology, it just eases
% the implications of complete locality unawareness.
medium
\end{tabular}
}
\end{center}
